Appendix

### 2025-10-21 manuscript_rmarkdown/manuscript.Rmd
Update lookup table.

Since the empirical central normality tests assesses whether the central part of a sequence is normally distributed,
we used $\kappa = 0.80$. Critical statistic values for central normality and empirical central
normality tests are shown are shown in Table \ref{tab:central-normality-critical-statistic} and Table 
\ref{tab:empirical-central-normality-critical-statistic}, respectively.

@@

usethis::use_data(
  central_normality_lookup_table,
  empirical_central_normality_lookup_table,
  two_sided_function_parameters, 
  internal = TRUE, 
  overwrite = TRUE
)
```

>>>>

Since the empirical central normality tests assesses whether the central part of a sequence is normally distributed,
we used $\kappa = 0.80$. Critical statistic values for $\kappa = 0.80$ and $\zeta = 0.10$ are shown in Table 
\ref{tab:empirical-central-normality-critical-statistic}.

@@

### 2025-10-21 manuscript_rmarkdown/manuscript_appendix.Rmd
Update lookup table.

```{r include = FALSE, eval = FALSE}
# This generates the table shown below.
.get_test_statistic_lookup_table(
  manuscript_dir = manuscript_dir,
  k = 0.80,
  for_manuscript = TRUE
)

@@

\begin{table}
\begin{center}
\caption{Critical values of test statistic $\tau_{\alpha, n, \kappa = 0.80}$ for
\textbf{central normality} at $\kappa = 0.80$, as a function of significance 
level $\alpha$ and number of instances $n$. The values in this table should be divided by $100$ before use.}
\label{tab:central-normality-critical-statistic}
\begin{tabular}{l | r r r r r r r r r}

@@

\midrule
    5 & 210.79 & 95.75 & 66.27 & 49.69 & 35.93 & 27.60 & 19.29 & 13.41 & 11.00 \\
   10 &  48.04 & 31.44 & 26.96 & 23.91 & 21.11 & 18.16 & 13.66 & 10.14 &  8.67 \\
   20 &  29.13 & 22.13 & 19.75 & 17.94 & 16.00 & 13.81 & 10.54 &  8.18 &  7.18 \\
   50 &  17.31 & 14.01 & 12.63 & 11.48 & 10.28 &  9.00 &  7.00 &  5.54 &  4.94 \\
  100 &  12.19 & 10.04 &  9.02 &  8.21 &  7.38 &  6.47 &  5.04 &  3.99 &  3.56 \\
  200 &   8.68 &  7.11 &  6.40 &  5.83 &  5.22 &  4.57 &  3.59 &  2.86 &  2.56 \\ 
  500 &   5.61 &  4.54 &  4.08 &  3.70 &  3.33 &  2.91 &  2.28 &  1.82 &  1.63 \\
 1000 &   3.93 &  3.19 &  2.87 &  2.60 &  2.33 &  2.05 &  1.61 &  1.29 &  1.15 \\
 2000 &   2.71 &  2.24 &  2.02 &  1.84 &  1.66 &  1.46 &  1.14 &  0.91 &  0.82 \\
 5000 &   1.73 &  1.42 &  1.28 &  1.17 &  1.05 &  0.92 &  0.72 &  0.58 &  0.52 \\
10000 &   1.22 &  1.00 &  0.90 &  0.82 &  0.74 &  0.65 &  0.51 &  0.41 &  0.37 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

```{r include = FALSE, eval = FALSE}
# This generates the table shown below.
.get_test_statistic_lookup_table(
  manuscript_dir = manuscript_dir,
  k = 0.80,
  for_manuscript = TRUE,
  with_outliers = TRUE
)

\begin{table}
\begin{center}
\caption{Critical values of test statistic $\tau_{\alpha, n, \kappa = 0.70}$ for
\textbf{empirical central normality} at $\kappa = 0.70$, as a function of significance 
level $\alpha$ and number of instances $n$.The values in this table should be divided by $100$ before use.}
\label{tab:empirical-central-normality-critical-statistic}
\begin{tabular}{l | r r r r r r r r r}

\midrule
    5 & 159.27 & 66.78 & 57.06 & 50.55 & 43.42 & 34.89 & 22.28 & 14.92 & 12.10 \\
   10 &  41.82 & 30.82 & 27.01 & 24.31 & 21.58 & 18.53 & 13.82 & 10.23 &  8.75 \\
   20 &  29.44 & 23.65 & 21.23 & 19.16 & 17.01 & 14.67 & 11.10 &  8.42 &  7.35 \\
   50 &  18.95 & 15.56 & 13.96 & 12.74 & 11.35 &  9.82 &  7.51 &  5.83 &  5.16 \\ 
  100 &  13.49 & 11.00 &  9.91 &  8.98 &  8.03 &  7.04 &  5.43 &  4.25 &  3.76 \\
  200 &   9.65 &  7.99 &  7.22 &  6.64 &  5.96 &  5.21 &  4.05 &  3.17 &  2.81 \\
  500 &   6.37 &  5.32 &  4.82 &  4.44 &  4.03 &  3.57 &  2.79 &  2.18 &  1.92 \\
 1000 &   4.64 &  3.95 &  3.65 &  3.39 &  3.11 &  2.78 &  2.20 &  1.73 &  1.53 \\
 2000 &   3.61 &  3.18 &  2.96 &  2.78 &  2.57 &  2.32 &  1.89 &  1.50 &  1.33 \\
 5000 &   2.78 &  2.48 &  2.36 &  2.24 &  2.11 &  1.95 &  1.66 &  1.39 &  1.25 \\
10000 &   2.39 &  2.18 &  2.08 &  2.00 &  1.91 &  1.81 &  1.59 &  1.39 &  1.28 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}

>>>>

```{r include = FALSE, eval = FALSE}
# This generates the table shown below.
.get_test_statistic_lookup_table_manuscript(
  manuscript_dir = manuscript_dir,
  kappa_lookup = 0.80,
  outlier_rate_lookup = 0.10
)

@@

\begin{table}
\begin{center}
\caption{Critical values of test statistic $\tau_{\alpha, n, \kappa = 0.80, \zeta = 0.10}$ for
central normality at $\kappa = 0.80$ and outlier rate $\zeta = 0.10$, as a function of significance 
level $\alpha$ and number of instances $n$. The values in this table should be divided by $100$ before use.}
\label{tab:empirical-central-normality-critical-statistic}
\begin{tabular}{l | r r r r r r r r r}

@@

\midrule
    5 & 210.38 & 82.23 & 59.47 & 48.68 & 38.71 & 29.28 & 19.75 & 13.71 & 11.15 \\
   10 &  43.22 & 33.68 & 29.26 & 26.04 & 22.96 & 19.62 & 14.37 & 10.50 &  8.89 \\
   20 &  31.31 & 25.35 & 22.61 & 20.58 & 18.23 & 15.64 & 11.51 &  8.61 &  7.49 \\
   50 &  19.97 & 16.53 & 14.83 & 13.33 & 11.77 & 10.11 &  7.60 &  5.85 &  5.16 \\
  100 &  14.01 & 11.57 & 10.30 &  9.31 &  8.31 &  7.22 &  5.49 &  4.29 &  3.78 \\
  200 &   9.87 &  8.15 &  7.39 &  6.73 &  6.02 &  5.28 &  4.06 &  3.16 &  2.80 \\
  500 &   6.30 &  5.34 &  4.87 &  4.49 &  4.08 &  3.60 &  2.80 &  2.17 &  1.92 \\
 1000 &   4.72 &  4.02 &  3.70 &  3.43 &  3.15 &  2.81 &  2.21 &  1.72 &  1.51 \\
 2000 &   3.61 &  3.18 &  2.96 &  2.78 &  2.57 &  2.32 &  1.88 &  1.49 &  1.31 \\
 5000 &   2.80 &  2.51 &  2.37 &  2.25 &  2.12 &  1.96 &  1.66 &  1.38 &  1.24 \\
10000 &   2.41 &  2.20 &  2.10 &  2.02 &  1.92 &  1.81 &  1.60 &  1.39 &  1.28 \\
\bottomrule
\end{tabular}
\end{center}
\end{table}
